\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.7in,top=0.4in,right=0.7in,bottom=0.6in]{geometry} 

\pagestyle{fancy}
% Clear the header and footer
\fancyhead{}
\fancyfoot{}

\fancyfoot[L]{\today}
\fancyfoot[R]{Page {\thepage}}
 % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%Headers
\def\name{Name}
\def\addressGeneral{Cairo, Egypt}
\def\phone{\href{tel:+201279711896}{Phone}}

\def\github{\URL{Github Full Url}{your github}}

\def\email{\URL{mailto:your email}{your email}}
\def\linkedin{\URL{LinkedIn full URL
}{your LinkedIn}}


\header{\name}{\addressGeneral}{\phone}{\email}{\linkedin}{\github} 

\sectionskip
\begin{Section}{Education}
	\begin{Education}{The American University in Cairo (AUC)}{Expected graduation: Month Year}{ Major: BS in Computer Engineering}{Your GPA}
	
	\end{Education} 
	
\end{Section}

% You can merge the next two sections in one section, called Experience
\begin{Section} {Industry Experience}

\begin{Job}{\large Google, London, UK} {August 2022-December 2022}
{ Software Engineer Intern}
\vspace{-0.1in}
\begin{itemize}
\itemsep -0.5em
\item One line bullet points of what you did.
\item Try to use X-Y-Z formula: Accomplished [X] as measured by [Y], by doing [Z].
\end{itemize}


\end{Job}

\end{Section}


\begin{Section} {Research Experience}


\begin{Job}{University Name and Location} {Dates} 
{ Undergraduate Researcher, The Security and Cryptography Laboratory(LASEC)}
\\[-0.5ex]
\textit{\normalsize Supervisor: supervisor name}
\vspace{-0.1in}
\begin{itemize}
\itemsep -0.5em
\item What you did 
		\end{itemize}
\end{Job}


\end{Section}

\begin{Section}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }
			Languages          & Proficient at [C++], Intermediate at [Python]\\\ 
							
			Tools  & Git, Linux, QT, ...\\  
		
		\end{tabular}

\end{Section}
\begin{Section}{Honors}
\begin{itemize}
\item Ranked 1st on \textbf{AUC Competitive Programming Contest} in 2020 \& 2021 (30+teams).
\item Led the team to rank as the 785th among 9000+ teams in \textbf{Google Hashcode 2021} (10th on Egypt).	 
\item Try to quantify your honor.
\end{itemize}
\end{Section}

\begin{Section}{Projects}
\begin{Project}{El-Modeer Linux Process Manager}{Group Project, Operating Systems Class, {\URL{Github URL to Project} {GitHub}}} {April 2023-May 2023}
\vspace{-0.01in}
\begin{itemize}
\itemsep -0.5em
\item Built a user-friendly CLI Linux process manager in \textbf{Rust} using \textbf{Tui} crate. It has a GUI processes tree.
\item Highligh the languanges and technolgieis by bolding it.

\end{itemize}
\end{Project}

\end{Section}





\begin{Section}{Extracurricular Activities}
\begin{Project}{Mathematics, Actuarial, Data Science Association; Mathematics Chairperson} \hfill{Jan. 2021-May 2021}
\vspace{-0.1in}
	\begin{itemize}
		\itemsep -0.5em %tighten up space
		\item ...
		
		
	\end{itemize}	
\end{Project}

\end{Section}

\end{document}
